The study targets the binary classification of malignant breast cancer with limited annotated data. Breast cancer is one of the common kinds of cancer and is the high cause of mortality among women. The classical identification methods require the specialist to  review the microscopic images of cytological images which is a tedious and time consuming process. The primary objective of the study is to develop the automated analysis model framework for classification from microscopic cytopathological images in an efficient manner. The model framework can be applied to perform the analysis at scale without need of the specialists. 
In order to perform classification, there exists various solutions, one of which includes training the convolutional neural networks from scratch which requires fine-tuning hyper-parameters and requires the annotated data in huge quantities. In this research, a framework has been provided to apply the transfer learning based solution from the source histopathological dataset to the target cytological images. The framework relies on transfer learning in which the weights obtained from the pre-training phase are used in the model training with both complete fine-tuning which targets the complete network and updates the weights using the backpropagation throughout the network  and partial-fine tuning, which only targets the last few layers as part of the experiments. 
The proposed framework contains a total eight phases as part of  the classification pipeline to provide the mechanism for the binary classification of breast cancers with transfer learning. All the implementation details of the study can be obtained from \footnote[1]{https://github.com/ma-shamshiri/Compatible-domain-Transfer-Learning} footnote link.
